---
title: "Depsy API scrape"
author: "Claire Kelling"
date: "6/27/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, I will construct the list of all of the packages that are both on Depsy and Cran. 

Now that we have all of the possible packages from the cran and depsy website (the intersection), we will pull all of the dependencies and create an edgelist from the neighbors listed in Depsy. 

We will also record features of the nodes, such as downloads and number of contributors. 

I will save this data for analysis at a later point.

```{r constructing nodes, message=FALSE}
library('RJSONIO')
library("rjson")
library("jsonlite")
load(file = "~/git/oss/data/oss/original/depsy/error_vector.Rdata")
load(file= '~/git/oss/data/oss/original/depsy/all_packages_cran.Rdata')

length(error_vec)/nrow(all_packages) #10.2% of the R packages on Cran are on Depsy
nrow(all_packages)-length(error_vec) #there are 9,810 R packages on Depsy

#Creating list of all packages on Cran and Depsy
depsy_packages <- all_packages[-error_vec,] #these are the 9,810 R packages on Depsy and cran
```



```{r}
# raw_data<-fromJSON("http://depsy.org/api/package/cran/A3")
# node_data <- matrix(nrow=9810,ncol=18)
# col_names(node_data) <- c("")
# 
# node_data$name <- c('citations_harv','citations_pmc', 'git_owner','git_repo_name','host', 'impact', 'impact_percentile', 'indegree', 'is_academic', 'language', 'name','neighborhood_size', 'num_authors', 'num_commits', 'num_committers', 'num_contribs', 'num_stars', 'downloads', 'citations', 'dep_rank', 'summary')
# 
# perc_downloads <- raw_data[[19]][[1]][[5]]
# num_downloads <- raw_data[[19]][[1]][[6]]
# perc_cit <- raw_data[[19]][[2]][[5]]
# num_cit <- raw_data[[19]][[2]][[6]]
# perc_deprank <- raw_data[[19]][[3]][[5]]
# num_deprank <- raw_data[[19]][[3]][[6]]
# summary <- raw_data[[20]]
# 
# raw_data<-fromJSON("http://depsy.org/api/package/cran/abctools")
# neighbors <- raw_data[[2]]

```

```{r nodal features}
source(file = "~/git/oss/src/ckelling/ScrapingCode/depsy/03_row_function.R")
node_mat <- c()
#for(i in 1:length(depsy_packages)){
for(i in 1:2){ 
 #scrape details from API using rjson
  print(i)
  new_row <- makeRow(depsy_packages[i,1])
  node_mat <- rbind(node_mat, new_row)
}
```


```{r edge list}
# edge_list <- c()
# for(i in 1:length(depsy_packages)){
#   #form edge list of all neighbor_id's that start with cran:
#   
# }
```

```{r}
save(node_mat, file = "~/git/oss/data/oss/original/depsy/node_mat.Rdata")
#save(edge_list, file = "~/git/oss/data/oss/original/depsy/edge_list.Rdata")
```
