---
title: 'Analysis of the Julia Ecosystem'
output: html_notebook
---

# Overview

[`Pkg.jl`](https://github.com/JuliaLang/Pkg.jl) is the standard package manager for Julia 1.0 and newer. It is a [`stdlib`](https://docs.julialang.org/en/latest/stdlib/Pkg/) of the [Julia language](https://julialang.org/). Packages in Julia can be installed from any source that has a valid repository. However, we only consider packages that have been *registered*. A registered package is one that is discoverable and installable from the official registry (presently [METADATA.jl](https://github.com/JuliaLang/METADATA.jl)). The Julia ecosystem provides a few tools obtaining relevant information about packages and their status. A few examples include (1) continous integration through [Travis C.I.](https://about.travis-ci.com/), code coverage through [Codecov](https://codecov.io/), documentation through [Documenter.jl](https://github.com/JuliaDocs/Documenter.jl) and hosted through [Github Pages](https://pages.github.com/). In addition, since the majority of repositories are [Github](https://github.com/) repositories additional information such as `LICENSE`, contributors (and contributions), and other characteristics can be compiled through the platform / interface (e.g., using [shields](https://shields.io/) in the `README` file). Dependencies in Julia are described in the `REQUIRE` file which is a component of any Julia package. One can access this file to parse the dependencies.

A Julia package is a repository which usually lives in [Github](https://github.com/) with very few exceptions. In some cases, repositories have been deleted making the package and metadata lost. An analysis of attrition found that these cases were very limited.

# Housekeeping

- Install [Licensee](https://github.com/benbalter/licensee/)
- Clone [METADATA.jl](https://github.com/JuliaLang/METADATA.jl) to `~/oss/data/oss/original/Julia/METADATA.jl` (last updated [7abfde6](https://github.com/JuliaLang/METADATA.jl/commit/7abfde68a874288b15ce5af80be9f305f267db6f) 2018-06-15)
- Set up a [Github API Personal Token](https://help.github.com/articles/creating-a-personal-access-token-for-the-command-line/)

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
# if you run that you don't need to use the here 
pacman::p_load(docstring, sdalr, configr, lubridate, dplyr, DBI, purrr,
               stringr, data.table, dtplyr, httr, jsonlite, rvest)
Sys.setenv(PATH = str_c(str_remove_all(string = Sys.getenv('PATH'),
                                       pattern = ':~/.gem/ruby/2.5.0/bin'),
                        '~/.gem/ruby/2.5.0/bin', sep = ':'))
Github_API_token = 'd77961efcd1dc0ae2b9ebb2fe6c9349e1a9c3da0'
# setwd(dir = rprojroot::find_rstudio_root_file())
```

# Obtain all packages and repositories

- Using the data in the official registry we obtain the name of the package and the repository
- Certain repositories are not available or re-direct to newer locations (these are updated)
- The name and updated registry is uploaded to the database (`jbsc/julia_name_repository`)

```{r basic_information}
filenames = str_c('./data/oss/original/Julia/METADATA.jl/',
                  list.files(path = './data/oss/original/Julia/METADATA.jl/') %>%
                    subset(!str_detect(string = ., pattern = '\\.')))
parse_registry = function(filename) {
  name = filename %>%
    str_sub(start = 39L)
  versions = str_c(filename, '/versions/') %>%
    list.files()
  if (is_empty(x = versions)) {
    latest_release = NA
    dependencies = NA
  } else {
    versions = versions[order(package_version(str_replace_all(string = versions,
                                                              c('-alpha' = '.0',
                                                                '-beta' = '.1',
                                                                '-dev' = '.0.'))))]
    requires = str_c(filename, '/versions/', versions, '/requires')
    latest_release = versions[length(x = versions)]
    dependencies = suppressWarnings(expr = readLines(con = requires[length(x = versions)]))
    dependencies = dependencies %>%
      subset(!str_detect(string = .,
                         pattern = '^julia')) %>%
      str_extract(pattern = '(?<=(^|@osx|@linux|@windows)\\s{0,1})\\w+')
    dependencies = dependencies %>%
      subset(!is.na(x = dependencies))
    if (is_empty(x = dependencies)) {
      dependencies = NA
    }
  }
  output = list(name = name,
                latest_release = latest_release,
                dependencies = dependencies)
  return(value = output)
  }
pkgs = map(.x = filenames,
           .f = parse_registry)
dependencies = function(pkg) {
  if (is_empty(x = pkg$dependencies)) {
    latest_release = NA
    dependency = NA
  } else {
    latest_release = pkg$latest_release
    dependency = pkg$dependencies
  }
  output = data.table(name = pkg$name,
                      latest_release = latest_release,
                      dependency = dependency)
  return(value = output)
}
pkg_dependency = map_df(.x = pkgs,
                        .f = dependencies)
upload_pkg_dependency = function(data) {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  dbWriteTable(conn = conn,
               name = 'julia_pkg_dependencies',
               value = data,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(expr = dbDisconnect(conn = conn))
  }
upload_pkg_dependency(data = pkg_dependency)
```

### Slug

```{r}
read_pkg_dependency = function() {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  output = dbReadTable(conn = conn,
                       name = 'julia_pkg_dependencies') %>%
    data.table()
  on.exit(expr = dbDisconnect(conn = conn))
  return(value = output)
  }
pkg_dependency = read_pkg_dependency()
helper = function(filename) {
  url = filename %>%
    readLines() %>%
    getElement(name = 1L)
    if (str_detect(string = url,
                   pattern = 'github.com')) {
      output = str_c('https://github.com/',
                     str_extract(string = url,
                                 pattern = '(?<=(com/))(\\w|-|\\.)+/(\\w|-)+(\\.jl)?'))
                      } else if (str_detect(string = url,
                                     pattern = 'gitlab.com')) {
                        output = str_c('https://gitlab.com/',
                                       str_extract(string = url,
                                                   pattern = '(?<=(com/))(\\w|-|\\.)+/(\\w|-)+(\\.jl)?'))
                        } else {
                          output = url
                          }
                      return(value = output)
}
urls = str_c(filenames, 'url', sep = '/') %>%
  map_chr(.f = helper)
urls = urls %>%
  str_replace(pattern = 'git://git.colberg.org/OnlineMoments.jl.git',
              replacement = 'https://git.colberg.org/peter/OnlineMoments.jl')
# file.size('./data/oss/original/Julia/github/CUBLAS')
urls[str_detect(string = urls,
           pattern = '/Twiddle(\\.jl)?$') %>%
  which()]
get_github_repos = function(repo) {
  slug = str_extract(string = repo,
                     pattern = '(?<=/)\\w+(\\.jl)?$')
  name = str_remove(string = slug,
                     pattern = '\\.jl$')
  destfile = str_c('./data/oss/original/Julia/github/',
                                 name)
  download.file(url = repo,
                destfile = destfile)
  fs = file.size(destfile)
  if (fs == 9L) {
    return()
  }
  if (fs < 1e3) {
    url = destfile %>%
      read_html() %>%
      html_node(css = 'a') %>%
      html_attr(name = 'href')
    get_github_repos(repo = url)
    }
  }
# for (url in urls[map_lgl(.x = list.files(path = './data/oss/original/Julia/github',
#                         full.names = TRUE),
#              .f = function(f) {
#                f %>%
#                  file.info() %>%
#                  pull(mtime) > mistake
#              })]) {
#   get_github_repos(repo = url)
#              }
for (repo in urls) {
  get_github_repos(repo = repo)
}
for (file in list.files(path = './data/oss/original/Julia/github',
                        full.names = TRUE)) {
  fs = file.size(file)
  # fs = file.info(file) %>%
  #   pull(mtime)
  # if (fs > mistake) {
  if ((fs < 1e3) & (fs > 9)) {
    print(file)
    url = file %>%
      read_html() %>%
      html_node(css = 'a') %>%
      html_attr(name = 'href')
    download.file(url = url,
                destfile = file)
    }
}

urls[str_detect(urls, 'FixedPoint')]
pkg_names[str_detect(urls, 'FixedPoint')]
helper = function(repo) {
  # repo = urls[10L]
  # repo = pkg_names[1]
  output = data.table()
  print(repo)
  fz = file.size(repo)
  if (fz == 9L) {
    return(value = output)
  } else {
    content_parsed = read_html(x = repo)
    url = content_parsed %>%
      html_node(xpath = "//meta[@property='og:url']/@content") %>%
      html_text()
    if (!str_detect(string = url,
                   pattern = 'github\\.com')) {
      return(value = output)
      }
    slug = content_parsed %>%
      html_nodes(css = '.public') %>%
      html_text(trim = TRUE)
    owner = slug %>%
      str_extract(pattern = '(\\w|-)+(?=/)')
    repo = slug %>%
      str_extract(pattern = '(?<=/)\\w+(\\.jl)?')
    kw = content_parsed %>%
      html_nodes(css = '.topic-tag-link') %>%
      html_text(trim = TRUE)
    if (is_empty(x = kw)) {
      kw = NA
    }
    description = content_parsed %>%
      html_nodes(css = '.mr-2') %>%
      html_text(trim = TRUE) %>%
      subset(. != '')
    if (is_empty(x = description)) {
      description = NA
    }
    output = data.table(owner = owner,
                        repository = url,
                        description = description,
                        keywords = str_c(kw, collapse = ', '))
  return(value = output)
    }
  }
pkg_names = str_c('./data/oss/original/Julia/github/',
                  str_extract(string = filenames,
                              pattern = '(?<=/)\\w+$'))
str_detect(pkg_names, 'AMD') %>%
  which()
pkg_names[26L]

list.files(path = './data/oss/original/Julia/github',
                                    full.names = TRUE)

basic_info = map_df(.x = list.files(path = './data/oss/original/Julia/github',
                                    full.names = TRUE),
                    .f = helper) %>%
  unique()
str_detect(pkg_names, 'FixedEffectModels') %>%
  which()
helper(pkg_names[608L])
NonGithub = basic_info$repository[!str_detect(basic_info$repository, 'github\\.com')]
```

# Obtaining the license information from the repository

The licenses were parsed detected by using Licensee 9.9.1 [2018-06-15]

```{r}
helper = function(repo) {
  filename = str_c('./data/oss/original/Julia/Licenses/',
                   str_extract(string = repo,
                               pattern = '(?<=\\.com/).*') %>%
                     str_remove(pattern = '\\.jl$') %>%
                     str_replace(pattern = '/',
                                 replacement = '_'),
                   '.txt')
  system(command = str_c('touch ', filename))
  if (file.info(filename)$size == 0L) {
    print(repo)
      system(command = str_c('OCTOKIT_ACCESS_TOKEN=',
                           Github_API_token,
                           ' licensee detect ',
                           repo,
                           ' > ',
                           filename))
      Sys.sleep(time = 5e-1)
      }
  }

for (repo in basic_info$repository) {
  helper(repo)
  }

files = list.files(path = './data/oss/original/Julia/Licenses',
                   full.names = TRUE)
files %>%
  subset(str_detect(files, 'AbaqusReader'))
parse_license_type = function(textfile) {
  owner = str_extract(string = textfile,
                      pattern = '(?<=Licenses/).*(?=_)')
  name = str_extract(string = textfile,
                     pattern = str_c('(?<=', owner, '_).*(?=.txt)'))
  license_text = readLines(con = textfile)
  if (is_empty(x = license_text)) {
    license = NA
    confidence = NA
  } else if (license_text[1] == 'License:  None') {
    license = 'BC'
    confidence = 1e2
  } else if (license_text[1] != 'License:        NOASSERTION') {
    license = str_remove(string = license_text[1],
                         pattern = '\\s*License:\\s+')
    confidence = license_text[str_detect(string =  license_text,
                                         pattern = '  Confidence:\\s+')]
    confidence = str_extract(string = confidence,
                             pattern = '\\d{1,3}.\\d{2}') %>%
      as.numeric()
  } else {
    license = license_text[str_detect(string = license_text,
                                    pattern = '  License:\\s+')]
    license = license[license != '  License:       NOASSERTION']
    if (!is_empty(x = license)) {
      license = str_remove(string = license,
                         pattern = '\\s+License:\\s+')
      confidence = str_extract(string = license_text,
                               pattern = '\\d{1,3}\\.\\d{2}') %>%
        na.omit() %>%
        getElement(name = 1L) %>%
        as.numeric()
    } else {
      license = str_detect(string = license_text,
                           pattern = '\\d{1,3}\\.\\d{2}') %>%
        which() %>%
        getElement(name = 1L)
      confidence = str_extract(string = license_text[license],
                               pattern = '\\d{1,3}\\.\\d{2}') %>%
        as.numeric()
      license = str_extract(string = license_text[license],
                            pattern = '.*(?=similarity)') %>%
        str_trim()
    }
  }
  output = data.table(owner = owner,
                      name = name,
                      license = license,
                      confidence = confidence)
  return(value = output)
  }
for (file in files) {
  print(file)
  parse_license_type(file)
}

licensee = map_df(.x = files,
                  .f = parse_license_type)

for (i in 1:nrow(x = julia_packages)) {
  if (with(data = julia_packages,
           expr = available[i] & (remote_platform[i] %in% 'github.com'))) {
    filename = str_c('./data/oss/original/Julia/Licenses/',
                     julia_packages$owner[i],
                     '_',
                     str_remove(string = julia_packages$name[i],
                                 pattern = '.jl$'),
                     '.txt')
    system(command = str_c('touch ', filename))
    if (file.info(filename)$size == 0L) {
      print(i)
      system(command = str_c('OCTOKIT_ACCESS_TOKEN=',
                           Github_API_token,
                           ' licensee detect ',
                           julia_packages$repository[i],
                           ' > ',
                           filename))
      Sys.sleep(time = 5e-1)
      }
    }
  }

basic_info = basic_info %>%
unique()


  url = response$url
  if (status_code(x = response) == 200L) {
    content_parsed = response %>%
      content(as = 'parsed')
    kw = content_parsed %>%
      html_nodes(css = '.topic-tag-link') %>%
      html_text(trim = TRUE)
    if (is_empty(x = kw)) {
      kw = NA
    }
    description = content_parsed %>%
      html_nodes(css = '.mr-2') %>%
      html_text(trim = TRUE) %>%
      subset(. != '')
    if (is_empty(x = description)) {
      description = NA
    }
    slug = content_parsed %>%
      html_nodes(css = '.public') %>%
      html_text(trim = TRUE)
    owner = slug %>%
      str_extract(pattern = '(\\w|-)+(?=/)')
    repo = slug %>%
      str_extract(pattern = '(?<=/)\\w+(\\.jl)?')
  } else {
    owner = url %>%
      str_extract(pattern = '(?<=\\.\\w{3}/)(\\w|-)+(?=/)')
    repo = url %>%
      str_extract(pattern = str_c('(?<=', owner, '/)\\w+(\\.jl)?'))
    kw = NA
    description = NA
    }
  output = data.table(owner = owner,
                      repository = url,
                      description = description,
                      keywords = str_c(kw, collapse = ', '))
  return(value = output)
  }
basic_information = map_df(.x = urls,
                           .f = helper) %>%
  mutate(name = str_extract(string = filenames,
                            pattern = '(?<=/)\\w+$'))
```

### Downloading the Github License Information
```{r}
basic_info$repository[1:10]
dir.create(path = './data/oss/original/Julia/Licenses_Text')
github_license = function(repository) {
  # repository = 'https://github.com/JuliaGraphs/LightGraphs.jl'
  print(repository)
  owner = str_extract(string = repository,
                      pattern = '(?<=/)[\\w-]+(?=/)')
  name = str_extract(string = repository,
                     pattern = str_c('(?<=', owner, '/).*'))
  license_file = str_c('https://api.github.com/repos/',
                         owner,
                         '/',
                         name,
                         '/',
                       'license') %>%
      GET(add_headers(Authorization = str_c('token ', Github_API_token))) %>%
      content(as = 'text', encoding = 'UTF-8') %>%
      fromJSON()
  license_type = license_file$license$spdx_id
  if (is_null(x = license_type)) {
    license_type = NA
  }
  if (!is_null(x = license_file$download_url)) {
    filename = str_c('./data/oss/original/Julia/Licenses_Text/',
                   owner,
                   '_',
                   name)
    system(command = str_c('touch ', filename))
    download.file(license_file$download_url, destfile = filename)
  }
  output = data.table(owner = owner,
                      name = str_extract(string = repository,
                                         pattern = str_c('(?<=',
                                                         owner,
                                                         '/).*(?=\\.jl?$)')),
                      license = license_type)
  return(value = output)
  }
output = map_df(.x = basic_info$repository,
                .f = github_license)
upload_julia_licenses_github = function(data) {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  dbWriteTable(conn = conn,
               name = 'julia_licenses_github',
               value = data,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(expr = dbDisconnect(conn = conn))
  }
upload_julia_licenses_github(data = output)
```

### Manual Parsing of Files
```{r}

all_pkgs = pkg_names %>%
  str_sub(start = 34L)
on_file = list.files(path = './data/oss/original/Julia/Licenses_Text') %>%
  str_extract(pattern = '(?<=_).*') %>%
  str_remove(pattern = '\\.jl$')
what_is_missing = setdiff(x = all_pkgs, y = on_file)
chk = basic_info %>%
  filter((repository %>%
            str_extract(pattern = str_c('(?<=', owner, '/).*')) %>%
            str_remove(pattern = '\\.jl$')) %in%
           what_is_missing)

manual = map_df(.x = list.files(path = './data/oss/original/Julia/Licenses_Text',
                                full.names = TRUE),
                .f = function(filename) {
                  # filename = './data/oss/original/Julia/Licenses_Text/JuliaGraphs_LightGraphs.jl'
                  print(filename)
                  slug = str_extract(string = filename,
                                     pattern = '(?<=Licenses_Text/).*') %>%
                    str_split(pattern = '_') %>%
                    unlist()
                  lines = readLines(con = filename,
                                        encoding = 'UTF-8')
                  if (is_empty(x = lines)) {
                    firstline = NA
                  } else {
                    if (any(str_detect(string = lines,
                                       pattern = 'is (licensed|distributed) under'))) {
                      firstline = lines %>%
                        subset(str_detect(string = lines,
                                       pattern = 'is (licensed|distributed) under')) %>%
                        getElement(name = 1L)
                    } else if (str_detect(string = lines[1L],
                                          pattern = 'Copyright')) {
                      firstline = lines %>%
                        subset(!str_detect(string = .,
                                          pattern = 'Copyright')) %>%
                        subset(. != '') %>%
                        getElement(name = 1L)
                    } else {
                      firstline = lines[1L]
                    }
                  }
                  output = data.table(owner = slug[1L],
                                      name = slug[2L],
                                      firstline = firstline)
                  return(value = output)
  })

license_parser = function(x) {
  if (is.na(x = x)) {
    output = NA
  } else if (str_detect(string = x, pattern = 'MIT')) {
    output = 'MIT'
  } else if (str_detect(string = x, pattern = 'Apache')) {
    output = 'Apache-2.0'
  } else if (str_detect(string = x, pattern = 'Simplified "2-clause" BSD')) {
    output = 'BSD-2-Clause'
  } else if (str_detect(string = x, pattern = '3-[Cc]lause') |
             str_detect(string = x, pattern = 'New BSD License')) {
    output = 'BSD-3-Clause'
  } else if (str_detect(string = x, pattern = 'Lesser GNU Public License, Version 3.0+') | str_detect(string = x, pattern = '\\[LGPL\\]')) {
    output = 'LGPL-3.0-or-later'
  } else if (str_detect(string = x, pattern = 'Mozilla Public License Version 2.0')) {
    output = 'MPL-2.0'
  } else if (str_detect(string = x, pattern = '(?i)GNU GENERAL PUBLIC LICENSE')) {
    output = 'GPL-3.0'
  } else if (str_detect(string = x, pattern = 'GNU Public License, Version 3.0+') |
             str_detect(string = x, pattern = 'GNU GPL')) {
    output = 'GPL-3.0-or-later'
  } else {
    output = NA
  }
  return(value = output)
  }

manual2 = manual %>%
  mutate(firstline = ifelse(test = str_detect(string = firstline,
                                              pattern = 'is (licensed|distributed) under'),
                            yes = str_extract(string = firstline,
                                              pattern = '(?<=(licensed|distributed) under).*'),
                            no = firstline),
         license = map_chr(.x = firstline,
                           .f = license_parser))
# Manual Fixes
manual2$license[manual2$name %in% 'VegaLite.jl'] = 'MIT'
manual2$license[manual2$name %in% 'CoreNLP.jl'] = 'GPL-3.0-or-later'
manual2$license[manual2$name %in% 'AffineInvariantMCMC.jl'] = 'GPL-2.0-or-later'
```


```{r}
read_github = function() {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  output = dbReadTable(conn = conn,
                       name = 'julia_licenses_github') %>%
    data.table()
  on.exit(expr = dbDisconnect(conn = conn))
  return(value = output)
}
github = read_github() %>%
  setnames(old = 'license', new = 'github')
licensee = licensee %>%
  setnames(old = 'license', new = 'licensee')
manual3 = manual2 %>%
  data.table() %>%
  mutate(name = str_remove(string = name, pattern = '\\.jl$')) %>%
  setnames(old = 'license', new = 'manual')
valid_license = data.table(repository = basic_info$repository) %>%
  mutate(owner = str_extract(string = repository,
                             pattern = '(?<=\\.com/)[\\w-]+(?=/)'),
         name = str_extract(string = repository,
                            pattern = str_c('(?<=', owner, '/).*')) %>%
           str_remove(pattern = '\\.jl$')) %>%
  merge(y = github) %>%
  merge(y = licensee) %>%
  merge(y = manual3) %>%
  mutate(license = ifelse(test = !is.na(x = github),
                          yes = github,
                          no = NA)) %>%
  mutate(license = ifelse(test = is.na(x = license),
                          yes = manual,
                          no = license)) %>%
  mutate(license = ifelse(test = is.na(x = license),
                          yes = licensee,
                          no = license))
licenses = function() {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  output = dbReadTable(conn = conn,
                       name = 'licenses') %>%
    data.table()
  return(value = output)
  on.exit(expr = dbDisconnect(conn = conn))
  }
licenses = licenses() %>%
  filter(osi) %>%
  pull(id)
valid_license = valid_license %>%
  mutate(osi = license %in% licenses)
upload_julia_licenses = function(data) {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  dbWriteTable(conn = conn,
               name = 'julia_licenses',
               value = data,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(expr = dbDisconnect(conn = conn))
  }
upload_julia_licenses(data = valid_license %>%
                        select(owner, name, repository, license, osi) %>%
                        data.table(key = c('owner', 'name')))
```

### Package Status
```{r}
pkg_status = valid_license %>%
  filter(osi & !(owner %in% 'JuliaArchive')) %>%
  mutate(slug = str_extract(string = repository,
                            pattern = '(?<=\\.com/).*')) %>%
  select(slug, repository, name)
pkg_status$name = pkg_status$name %>%
  recode('SNN' = 'SpikingNetworks',
         'ANN' = 'ImputationAlgamest',
         'AMG' = 'AlgebraicMultigrid',
         'fstformat' = 'FstFileFormat')
pkg_status$name = pkg_status$name %>%
  recode('SNN' = 'SpikingNetworks',
         'ANN' = 'ImputationAlgamest',
         'AMG' = 'AlgebraicMultigrid',
         'fstformat' = 'FstFileFormat')
pkg_dependency$name = pkg_dependency$name %>%
  recode('SNN' = 'SpikingNetworks',
         'ANN' = 'ImputationAlgamest',
         'AMG' = 'AlgebraicMultigrid',
         'fstformat' = 'FstFileFormat')
valid_license$name = valid_license$name %>%
  recode('SNN' = 'SpikingNetworks',
         'ANN' = 'ImputationAlgamest',
         'AMG' = 'AlgebraicMultigrid',
         'fstformat' = 'FstFileFormat')
pkg_dependency$dependency = pkg_dependency$dependency %>%
  recode('SNN' = 'SpikingNetworks',
         'ANN' = 'ImputationAlgamest',
         'AMG' = 'AlgebraicMultigrid',
         'fstformat' = 'FstFileFormat')
pkg_dependency = pkg_dependency %>%
  rbind(data.table(name = 'ImputationAlgamest',
                   latest_release = '0.0.2',
                   dependency = NA)) %>%
  rbind(data.table(name = 'SpikingNetworks',
                   latest_release = '0.0.4',
                   dependency = NA)) %>%
  unique() %>%
  data.table(key = c('name', 'dependency'))
pkg_dependency = pkg_dependency %>%
  filter(name %in% unique(valid_license$name))
setdiff(pkg_status$name, pkg_dependency$name)

upload_
upload_pkg_dependency(data = pkg_dependency)
upload_julia_licenses(data = valid_license)

# Renamed a few packages for consistency
# SNN to SpikingNetworks
# ANN to ImputationAlgamest
# AMG to AlgebraicMultigrid
# fstformat to FstFileFormat
```

# Package Status
```{r}
read_pkg_dependency = function() {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  output = dbReadTable(conn = conn,
                       name = 'julia_pkg_dependencies') %>%
    data.table()
  on.exit(expr = dbDisconnect(conn = conn))
  return(value = output)
  }
read_valid_license = function() {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  output = dbReadTable(conn = conn,
                       name = 'julia_licenses') %>%
    data.table()
  on.exit(expr = dbDisconnect(conn = conn))
  return(value = output)
  }

pkg_dependency = read_pkg_dependency()
valid_license = read_valid_license()

pkg_status = valid_license %>%
  filter(osi) %>%
  select(name, repository) %>%
  mutate(slug = str_extract(string = repository,
                            pattern = '(?<=github\\.com/).*')) %>%
  merge(y = pkg_dependency %>%
          select(name, latest_release) %>%
          unique(),
        by = 'name')
travis_ci = function(slug) {
  # slug = 'sam81/BDF.jl'
  slug = 'jstrube/LCIO.jl'
  output = FALSE
  try(expr = {
    ci = GET(url = str_c('https://api.travis-ci.org/repos/', slug, '/branches'),
                 add_headers(c(Accept = 'application/json',
                               Authorization = 'token DRt1TjjDmPG4wX8bq0YqVg'))) %>%
      content(as = 'text', encoding = 'UTF-8') %>%
      fromJSON()
    branches = ci$branches
    release_0.6 = branches$started_at >= as.Date('2017-06-19')
    valid = map_lgl(.x = branches$config$julia,
            .f = function(x) {any(str_detect(string = x, pattern = '0\\.6'))}) |
      (release_0.6 & map_lgl(.x = branches$config$julia,
            .f = function(x) {any(str_detect(string = x, pattern = 'release'))}))
    branches = branches %>%
      subset(valid)
    commits = ci$commits %>%
      subset(valid)
    if (any(branches$state %in% 'passed')) {
      output = TRUE
    } else {
      for (job in branches$id) {
        response = GET(url = str_c('https://api.travis-ci.org/builds',
                                   job,
                                   sep = '/'),
                       add_headers(c(Accept = 'application/json',
                                     Authorization = 'token DRt1TjjDmPG4wX8bq0YqVg'))) %>%
          content(as = 'text', encoding = 'UTF-8') %>%
          fromJSON()
        output = any(response$matrix %>%
                       subset(.$config$julia %in% '0.6') %>%
                       getElement(name = 'result') == 0L,
                     na.rm = TRUE)
        if (output) {
          break
          }
        }
      }
    },
    silent = TRUE)
  return(value = output)
  }

print(travis_ci(slug = '4gh/WorldBankData.jl'))

get_last_commit = function(slug) {
  last_commit = str_c('https://api.github.com/repos',
                      slug,
                      'commits',
                      sep = '/') %>%
    GET(add_headers(Authorization = str_c('token ', Github_API_token))) %>%
    content(as = 'text', encoding = 'UTF-8') %>%
    fromJSON()
  output = data.table(slug = slug,
                      last_commit = last_commit$commit$committer$date[1L] %>%
                        as.Date())
  }

last_commit = map_df(.x = pkg_status$slug,
                     .f = get_last_commit)

pkg_status = pkg_status %>%
  mutate(status = map_lgl(.x = slug,
                          .f = travis_ci))
to_fix = pkg_status2 %>%
  filter(!status | is.na(x = status)) %>%
  mutate(status = map_lgl(.x = slug,
                          .f = travis_ci))
pkg_status3 = merge(x = pkg_status2,
                    y = to_fix,
                    by = setdiff(names(pkg_status2),
                                 'status'),
                    all.x = TRUE) %>%
  mutate(status.x = ifelse(test = is.na(status.x),
                           yes = status.y,
                           no = status.x)) %>%
  mutate(status.x = ifelse(test = !is.na(status.y),
                           yes = status.y,
                           no = status.x)) %>%
  select(-status.y) %>%
  data.table() %>%
  setnames(old = 'status.x', new = 'status') %>%
  mutate(status = ifelse(test = str_detect(string = slug,
                                           pattern = '^JuliaArchive/'),
                         yes = FALSE,
                         no = status))

deprecated = basic_info %>%
  filter(str_detect(string = description,
                                 pattern = '(?i)(deprecated)')) %>%
  pull(repository) %>%
  unique()
pkg_status3 = pkg_status3 %>%
  mutate(status = ifelse(test = repository %in% deprecated,
         yes = FALSE,
         no = status))
table(pkg_status3$status)

wip = basic_info %>%
  filter(str_detect(string = description,
                                 pattern = '(?i)WIP'))

pkg_status$status[pkg_status$name %in% 'LCIO'] = TRUE # Manual fix

read_pkg_status = function(data) {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  output = dbReadTable(conn = conn,
              name = 'julia_pkg_status') %>%
    data.table()
  on.exit(expr = dbDisconnect(conn = conn))
  return(value = output)
  }
pkg_status = read_pkg_status()

upload_pkg_status = function(data) {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  dbWriteTable(conn = conn,
               name = 'julia_pkg_status',
               value = data,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(expr = dbDisconnect(conn = conn))
  }
upload_pkg_status(pkg_status)

length(intersect(pkg_status3 %>%
                   filter(status) %>%
                   pull(name),
                 valid_license %>%
                   filter(osi) %>%
                   pull(name)))
helper = function(idx) {
  activity = basic_information$weeks[[idx]] %>%
    filter(c > 0L)
  time_period = activity$w
  adc = colSums(activity[,2:4])
  output = data.table(slug = slug,
                      contributor = basic_information$author$login[idx],
                      start_date = as.Date(as.POSIXct(time_period[1L],
                                                      origin = '1970-01-01')),
                      end_date = as.Date(as.POSIXct(time_period[length(
                        x = time_period)],
                        origin = '1970-01-01')),
                      additions = adc[1L],
                      deletions = adc[2L],
                      commits = adc[3L])
  return(value = output)
  }
parser = function(basic_information) {
  output = map_df(.x = 1L:nrow(x = basic_information),
                  .f = helper)
  }
activity = basic_information$weeks[[1]]
names(chk)
parse_activity = function(activity) {
  activity = activity %>%
    filter(c > 0)
  output = data.table(start_date = as.Date(as.POSIXct(activity$w[1L],
                                                      origin = '1970-01-01')),
                      end_date = as.Date(as.POSIXct(activity$w[length(
                        x = activity$w)],
                        origin = '1970-01-01')),
                      additions = sum(activity$a),
                      deletions = sum(activity$d),
                      commits = sum(activity$c))
  return(value = output)
  }
# slug = 'JuliaStats/StatsBase.jl' # Change the slug to the owner/repo form
chk = map_df(.x = basic_information$weeks,
             .f = parse_activity)

rm(wip)
parse_github_repo = function(slug) {
  # slug = slugs[977]
  baseurl = 'https://api.github.com'
  endpoint = 'repos'
  contributions = 'stats/contributors'
  response = str_c(baseurl,
                   endpoint,
                   slug,
                   contributions,
                   sep = '/') %>%
    GET(add_headers(Authorization = str_c('token ', Github_API_token)))
  basic_information = response %>%
    content(as = 'text') %>%
    fromJSON() %>%
    subset(.$author$type %in% 'User')
  if (is_empty(x = basic_information)) {
    output = data.table(user = NA,
                        slug = slug,
                        start_date = NA,
                        end_date = NA,
                        additions = NA,
                        deletions = NA,
                        commits = NA)
  } else {
    output = data.table(user = basic_information$author$login) %>%
    mutate(slug = slug) %>%
    cbind(map_df(.x = basic_information$weeks,
                 .f = parse_activity))
  }
  return(value = output)
  Sys.sleep(time = 1L)
  }
rm(response)
slugs = pkg_status %>%
  filter(status) %>%
  pull(slug)

slug = slugs[1]

for(slug in slugs) {
  print(slug)
  try(a = parse_github_repo(slug = slugs[1]))
}
rm(basic_information)
output = map_df(.x = slugs,
                .f = parse_github_repo)
upload_contributions
upload_contributions = function(data) {
  conn = con_db(dbname = 'oss',
                pass = get_my_password())
  dbWriteTable(conn = conn,
               name = 'julia_contributions',
               value = data,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(expr = dbDisconnect(conn = conn))
  }
upload_contributions(data = output)

chk = parse_github_repo(slug = slugs[977])
chk = parse_github_repo(slug = slugs[2])

chk = map_lgl(pkg_status$slug[39], travis_ci)

pkg_status2 = pkg_status %>%
  unique() %>%
  merge(y = last_commit,
        by = 'slug') %>%
  unique()
pkg_status2 = pkg_status2 %>%
  mutate(status = ifelse(test = str_detect(string = slug,
                                           pattern = '^JuliaArchive/'),
                         yes = FALSE,
                         no = status))

verify = pkg_status %>%
  filter(!status)

print(travis_ci(slug = 'Keno/Cxx.jl'))



 builds = GET(url = str_c('https://api.travis-ci.org/repos/', slug, '/builds'),
               add_headers(c(Accept = 'application/json',
                             Authorization = 'token DRt1TjjDmPG4wX8bq0YqVg'))) %>%
    content(as = 'text', encoding = 'UTF-8') %>%
    fromJSON()
}

```







helper = function(i) {
  if (i == 2L) {
    output = data.table(a = 1:3, b = 1:3)
  } else {
    output = data.table()
  }
  return(output)
}
a = map_df(.x = 1:3, .f = helper)
urls[str_detect(string = urls, 'ca') %>%
  which()]
responses = 
```

urls


```{r}
pkg_status = data.table(name = julia_support$name,
                        status = NA,
                        criteria = NA) %>%
  mutate(status = ifelse(test = julia_support$julia_max %in% '0.7',
                         yes = 'Development',
                         no = status),
         criteria = ifelse(test = julia_support$julia_max %in% '0.7',
                           yes = '0.7 Only',
                           no = criteria)) %>%
  mutate(status = ifelse(test = is.na(x = julia_support$julia_max),
                         yes = 'Unmaintained',
                         no = status),
         criteria = ifelse(test = is.na(x = julia_support$julia_max),
                           yes = 'Not Installable',
                           no = criteria))
travis = 
```

table(is.na(pkg_status$status))

pkgs[[49L]]
for (i in 1:length(pkgs)) {
  print(i)
  julia_min_max(pkg = pkgs[[i]])
}

str_detect(string = filenames,
           pattern = '/StatsBase$') %>%
  which()
filenames[c(687,1312,1764)]
parse_registry(filename = filenames[1L])
parse_registry(filename = filenames[1764L])
}
```
