---
title: 'Scraper: `Pkg`'
root.dir: ~/oss
output:
  html_notebook: 
    code_folding: hide
    toc: yes
---

# Overview

[`Pkg.jl`](https://github.com/JuliaLang/Pkg.jl) is the standard package manager for Julia 1.0 and newer. It is a [`stdlib`](https://docs.julialang.org/en/latest/stdlib/Pkg/) of the [Julia language](https://julialang.org/). Packages in Julia can be installed from any source that has a valid repository. However, we only consider packages that have been *registered*. A registered package is one that is discoverable and installable from the official registry (presently [METADATA.jl](https://github.com/JuliaLang/METADATA.jl)). The Julia ecosystem provides a few tools obtaining relevant information about packages and their status. A few examples include (1) continous integration through [Travis C.I.](https://about.travis-ci.com/), code coverage through [Codecov](https://codecov.io/), documentation through [Documenter.jl](https://github.com/JuliaDocs/Documenter.jl) and hosted through [Github Pages](https://pages.github.com/), and additional continous integration for releases through the [PackageEvaluator.jl](https://pkg.julialang.org/). In addition, since the majority of repositories are [Github](https://github.com/) repositories additional information such as `LICENSE`, contributors (and contributions), and other characteristics can be easily communicated through the platform / interface (e.g., using [shields](https://shields.io/) in the `README` file). Dependencies in Julia are described in the `REQUIRE` file which is a component of any Julia package. One can access this file to parse the dependencies.

A Julia package is a repository which usually lives in [Github](https://github.com/); only two packages out of 2,032 were hosted in a different platform (one in [Gitlab](https://gitlab.com/) and one in [colberg.org](https://colberg.org/)). In some cases, repositories have been deleted making the package and metadata lost. An analysis of attrition found that these cases were only 5 out of 2,032.

# Housekeeping

- Install [Licensee](https://github.com/benbalter/licensee/)
- Clone [METADATA.jl](https://github.com/JuliaLang/METADATA.jl) to `~/oss/data/oss/original/Julia/METADATA.jl` (last updated [7abfde6](https://github.com/JuliaLang/METADATA.jl/commit/7abfde68a874288b15ce5af80be9f305f267db6f) 2018-06-15)
- Set up a [Github API Personal Token](https://help.github.com/articles/creating-a-personal-access-token-for-the-command-line/)

```{r setup}
pacman::p_load(docstring, sdalr, DBI, dplyr, data.table, dtplyr)
some_data = function() {
  #' Getting some_data from the database.
  #'
  #' @example some_data()
  conn = con_db(dbname = 'jbsc',
                pass = get_my_password())
  output = dbReadTable(conn = conn,
                       name = '') %>%
    data.table()
  on.exit(dbDisconnect(conn = conn))
  return(value = output)
  }

library(rvest)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
# if you run that you don't need to use the here 
pacman::p_load(docstring, sdalr, configr, dplyr, DBI, purrr, stringr,
               data.table, dtplyr, httr, jsonlite)
Sys.setenv(PATH = str_c(str_remove_all(string = Sys.getenv('PATH'),
                                       pattern = ':~/.gem/ruby/2.5.0/bin'),
                        '~/.gem/ruby/2.5.0/bin', sep = ':'))
Github_API_token = 'd77961efcd1dc0ae2b9ebb2fe6c9349e1a9c3da0'
# setwd(dir = rprojroot::find_rstudio_root_file())
```

# Obtaining all registered packages

The registry `METADATA.jl` contains all registered packages. It is better to work with a local copy since there are too many files for the Github API to handle and by using version control one can retrieve the exact version used in the language.

- Data: db: `jbsc`, name: `julia_packages`
  - Variables: `owner`, `name`, `repository`, `available`, `remote_platform`
  - Last updated: `2018-06-15 14:05:00 EDT`

```{r}
owner_name_repo = function(){
  #' Obtains the Owner, Name, and Repository for all registered packages.
  #'
  #' @description Owner, name, and repositories for all registered packages found
  #' from `~/oss/data/oss/original/Julia/METADATA.jl/`. To obtain the latest,
  #' make sure the repository is synched.

  #' @usage owner_name_repo()
  #' @return Writes the data to 'id.julia_packages'
  packages = str_c('~/oss/data/oss/original/Julia/METADATA.jl/',
                   list.files(path = '~/oss/data/oss/original/Julia/METADATA.jl'),
                   '/url')
  packages = str_extract(string = packages,
                         pattern = '(?<=METADATA\\.jl/).*(?=/)')
  julia_packages = julia_packages %>%
    setnames(old = 'name', new = 'repo') %>%
    mutate(name = packages)
  
  get_description = function(repository) {
    # repository = name_description$repository[16]
    response = repository %>%
      GET()
    if (status_code(x = response) == 200L) {
      description = read_html(x = response) %>%
        html_nodes(css = '.mr-2') %>%
        html_text()
      if (length(x = description) == 4L) {
        description = str_trim(string = description[4L])
        } else {
          description = ''
        }
      output = data.table(repository = repository,
                          available = TRUE,
                          description = description)
    } else {
      output = data.table(repository = repository,
                          available = FALSE,
                          description = '')
    }
    return(value = output)
  }
  arg = get_description(repository = 'https://github.com/rdeits/DrakeVisualizer.jl')
  
  crazy = vector(mode = 'list', length = nrow(julia_packages))
  for (i in 1:length(x = crazy)) {
    if (description$available[i]) {
      crazy[[i]] = description[i,]
    } else {
      print(i)
      crazy[[i]] = get_description(repository = julia_packages$repository[i])
      Sys.sleep(time = 5e-1)
    }
  }
  which(is_empty(x = crazy))
  description = map_df(.x = julia_packages$repository,
                       .f = get_description)
    
  is_empty(x = crazy[[1000]])
  crazy[[1000]]
    mutate(description = get_description(repository = repository)) %>%
    select(name, description)
  
  # Collect the URL for all packages excluding the `Rproj` and `README.md` files.
  packages = packages[!str_detect(string = packages, pattern = '(.Rproj|.md)')]
  repositories = packages %>%
    map_chr(.f = function(file) {
      read.table(file = file, as.is = TRUE) %>%
      getElement(name = 'V1')
    }) %>%
    str_replace(pattern = 'git://', replacement = 'https://') %>%
    str_replace(pattern = '(?<=.jl).git$', replacement = '')
  output = map_df(.x = repositories,
                  .f = function(url) {
                    output = GET(url = url)
                    output = data.table(repository = output$url,
                                        available = status_code(output) != 404L)
                    return(value = output)
                    })
  output = output %>%
    mutate(owner = str_extract(string = repository,
                               pattern = '(?<=.(com|org)/).*(?=/)'),
           repo = str_extract(string = repository,
                              pattern = str_extract(string = repository,
                                                    pattern = str_c('(?<=',
                                                                    owner,
                                                                    '/).*(?=.jl)'))),
           remote_platform = str_extract(string = repository,
                                        pattern = '[:alnum:]+(.com|.org)')) %>%
    unique() %>%
    mutate(name = str_extract(string = repository,
                              pattern = str_extract(string = repository,
                                                    pattern = str_c('(?<=', owner, '/).*(?=$)')))) %>%
    data.table() %>%
    setcolorder(neworder = c('owner', 'name', 'repository', 'available'))
  conn = con_db(dbname = 'jbsc',
                pass = get_my_password())
  dbWriteTable(con = conn,
               name = 'julia_packages',
               value = output,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(?dbDisconnect(conn = conn))
  }
# owner_name_repo() # last run with 7abfde6
julia_packages = function() {
  conn = con_db(dbname = 'jbsc',
                pass = get_my_password())
  julia_packages = dbReadTable(conn = conn,
                               name = 'julia_packages') %>%
    data.table()
  on.exit(dbDisconnect(conn = conn))
  return(value = julia_packages)
  }
julia_packages = julia_packages()

system(command = 'licensee detect "" > tmp.txt')
df = data.frame(a = 'MIT License', stringsAsFactors = F)
for (i in c('',
            'https://github.com/Nosferican/NCEI.jl')) {
  print(str_c('licensee ', i, '> ', str_split(i, '/')[[length(str_split(i, '/'))]],  '.txt'))
  # system(str_c('licensee ', i, '> ', str_split(i, '/')[[length(str_split(i, '/'))]],  '.txt') )
  }
```

```{r}
library(rvest)
pkg_eval_license = function() {
  response = 'https://pkg.julialang.org/' %>%
    read_html()
  pkgs = response %>%
    html_nodes(css = '.pkgnamedesc') %>%
    html_text() %>%
    str_extract(pattern = '\\s*[:alnum:]*') %>%
    str_trim()
  license_owner = response %>%
    html_nodes(css = '.pkgvertest') %>%
    html_text() %>%
    str_replace_all(pattern = '[\\s|\n]+', replacement = ' ') %>%
    str_split(pattern = '/') %>%
    map_df(.f = function(x) {
      x = unlist(x = x)[1:2] %>%
        str_trim()
      output = data.table(owner = str_extract(string = x[2], pattern = '(?<=Owner: ).*'),
                      license = str_extract(string = x[1], pattern = '.*(?= license)') %>%
                        str_trim())
    })
  pkg_eval_license = cbind(pkgs, license_owner) %>%
    data.table(key = c('owner', 'pkgs')) %>%
    setnames(old = 'pkgs', new = 'name') %>%
    setnames(old = 'license', new = 'pkg_eval') %>%
    setcolorder(neworder = c('owner', 'name', 'pkg_eval')) %>%
    select(owner, name, license) %>%
    data.table(key = c('owner', 'name')) %>%
    setnames(old = 'license', new = 'licensee') %>%
    merge(output) %>%
    merge(y = data.table(select(.data = julia_packages, owner, name, repository))) %>%
    mutate(pkg_eval = str_replace_all(string = pkg_eval,
                                      pattern = ' v2',
                                      replacement = '-2.0')) %>%
    mutate(pkg_eval = str_replace_all(string = pkg_eval,
                                      pattern = ' v3',
                                      replacement = '-3.0')) %>%
    mutate(pkg_eval = str_replace_all(string = pkg_eval,
                                      pattern = 'zlib',
                                      replacement = 'Zlib')) %>%
    mutate(pkg_eval = str_replace_all(string = pkg_eval,
                                      pattern = 'BSD 3-clause',
                                      replacement = 'BSD-3-Clause')) %>%
    mutate(pkg_eval = str_replace_all(string = pkg_eval,
                                      pattern = 'BSD 2-clause',
                                      replacement = 'BSD-2-Clause')) %>%
    mutate(pkg_eval = str_replace_all(string = pkg_eval,
                                      pattern = 'LGPL-3.0.0',
                                      replacement = 'LGPL-3.0')) %>%
    mutate(pkg_eval = str_replace_all(string = pkg_eval,
                                      pattern = 'Apache',
                                      replacement = 'Apache-2.0'))
  
}

conn = con_db(dbname = 'oss',
              pass = get_my_password())
  dbWriteTable(conn = conn,
               name = 'licenses',
               value = licenses,
               )
  dbDisconnect(conn = conn)
  ?dbWriteTable
  
conn = con_db(pass = get_my_password())
  dbWriteTable(conn = conn,
               name = 'license_comparison',
               value = verify,
               row.names = FALSE,
               overwrite = TRUE)
  dbDisconnect(conn = conn)


verify2 = verify %>%
    mutate(sad = licensee == pkg_eval)
  verify3 = verify2 %>%
    filter(!sad)
  conn = con_db(pass = get_my_password())
  dbWriteTable(conn = conn,
               name = 'license_comparison',
               value = verify,
               row.names = FALSE,
               overwrite = TRUE)
  dbDisconnect(conn = conn)
```

# Obtaining the license information from the repository

The licenses were parsed detected by using Licensee 9.9.1 [2018-06-15]

```{r}
# for (i in 1:nrow(x = julia_packages)) {
#   if (with(data = julia_packages,
#            expr = available[i] & (remote_platform[i] %in% 'github.com'))) {
#     filename = str_c('./data/oss/original/Julia/Licenses/',
#                      julia_packages$owner[i],
#                      '_',
#                      str_remove(string = julia_packages$name[i],
#                                  pattern = '.jl$'),
#                      '.txt')
#     system(command = str_c('touch ', filename))
#     if (file.info(filename)$size == 0L) {
#       print(i)
#       system(command = str_c('OCTOKIT_ACCESS_TOKEN=',
#                            Github_API_token,
#                            ' licensee detect ',
#                            julia_packages$repository[i],
#                            ' > ',
#                            filename))
#       Sys.sleep(time = 5e-1)
#       }
#     }
#   }

parse_license_type = function(textfile) {
  # textfile = files[107]
  owner = str_extract(string = textfile,
                      pattern = '(?<=Licenses/).*(?=_)')
  name = str_extract(string = textfile,
                     pattern = str_c('(?<=', owner, '_).*(?=.txt)'))
  license_text = readLines(con = textfile)
  if (is_empty(x = license_text)) {
    license = NA
    confidence = NA
  } else if (license_text[1] == 'License:  None') {
    license = 'BC'
    confidence = 1e2
  } else if (license_text[1] != 'License:        NOASSERTION') {
    license = str_remove(string = license_text[1],
                         pattern = '\\s*License:\\s+')
    confidence = license_text[str_detect(string =  license_text,
                                         pattern = '  Confidence:\\s+')]
    confidence = str_extract(string = confidence,
                             pattern = '\\d{1,3}.\\d{2}') %>%
      as.numeric()
  } else {
    license = license_text[str_detect(string = license_text,
                                    pattern = '  License:\\s+')]
    license = license[license != '  License:       NOASSERTION']
    if (!is_empty(x = license)) {
      license = str_remove(string = license,
                         pattern = '\\s+License:\\s+')
      confidence = str_extract(string = license_text,
                               pattern = '\\d{1,3}\\.\\d{2}') %>%
        na.omit() %>%
        getElement(name = 1L) %>%
        as.numeric()
    } else {
      license = str_detect(string = license_text,
                           pattern = '\\d{1,3}\\.\\d{2}') %>%
        which() %>%
        getElement(name = 1L)
      confidence = str_extract(string = license_text[license],
                               pattern = '\\d{1,3}\\.\\d{2}') %>%
        as.numeric()
      license = str_extract(string = license_text[license],
                            pattern = '.*(?=similarity)') %>%
        str_trim()
    }
  }
  output = data.table(owner = owner,
                      name = name,
                      license = license,
                      confidence = confidence)
  return(value = output)
}

conn = con_db(dbname = 'jbsc',
              pass = get_my_password())
licenses = dbReadTable(conn = conn,
                       name = 'prj_licenses')
dbDisconnect(conn = conn)
df
files = str_c('./data/oss/original/Julia/Licenses/',
                        list.files(path = './data/oss/original/Julia/Licenses/'))

chk = map_df(.x = files,
             .f = parse_license_type) %>%
  plyr::ddply(.variables = 'name',
              .fun = function(df) {
                return(value = head(df, 1))
              })
why = chk %>%
  filter(confidence < 75) %>%
  merge(y = select(licenses, name, license_text))

custom_parser = licenses %>%
  select(name, license_text) %>%
  mutate(keypart = str_extract(string = license_text,
                               pattern = '(?<=package is licensed under the ).*(?=License)'))

id_kw = function(kw) {
  if (str_detect(string = kw,
                 pattern = 'MIT')) {
    output = 'MIT'
    } else if (str_detect(string = kw,
                          pattern = '3-claused BSD ')) {
      output = 'BSD-3'
    } else if(str_detect())
  }


a = head(licenses)

for (i in 1:length(files)) {
  print(i)
  parse_license_type(files[i])
}

julia_specific = function(repository) {
  repository = basic_info$repository[1L]
  repo
  # repository = basic_info$repository[1]
  repository = 'https://github.com/JuliaData/DataFrames.jl'
  owner = str_extract(string = repository,
                      pattern = '(?<=/)\\w+(?=/)')
  name = str_extract(string = repository,
                     pattern = str_c('(?<=', owner, '/).*'))
  filename = str_c('./data/oss/original/Julia/Licenses_Text/',
                   owner,
                   '_',
                   name)
  system(command = str_c('touch ', filename))
  license_file = str_c('https://api.github.com/repos/',
                         owner,
                         '/',
                         name,
                         '/',
                       'license') %>%
      GET(add_headers(Authorization = str_c('token ', Github_API_token))) %>%
      content(as = 'text', encoding = 'UTF-8') %>%
      fromJSON()
  license_type = license_file$license$spdx_id
  if (is_null(x = license_type)) {
    license_type = NA
  }
  download.file(license_file$download_url, destfile = filename)
  output = data.table(owner = owner,
                      name = str_extract(string = repository,
                                         pattern = str_c('(?<=',
                                                         owner,
                                                         '/).*(?=\\.jl?$)')),
                      license = license_type)
  repository
  Github_API_token
  
  
  license_file = str_c('https://api.github.com/repos/',
                         owner,
                         '/',
                         name,
                         '.jl/license') %>%
      # This is my Personal Token for this project.
      GET(add_headers(Authorization = str_c('token ', Github_API_token))) %>%
      content(as = 'text', encoding = 'UTF-8') %>%
      fromJSON()
  /repos/:owner/:repo/license
}



for (i in 1:length(files)) {
  print(i)
  parse_license_type(files[i])
}

chk = map_df(.x = str_c('./data/oss/original/Julia/Licenses/',
                        list.files(path = './data/oss/original/Julia/Licenses/'))[1:10],
             .f = parse_license_type)
  
  
  license_text[1]
  if (license_text[1] == 'License:        NOASSERTION') {
    license = str_extract(string = license_text[7],
                          pattern = '.*(?= similarity)') %>%
      str_trim()
    confidence = str_extract(string = license_text[7],
                             pattern = '\\d{2,3}.\\d{2}') %>%
      as.numeric()
  } else if (license_text == 'License:  None') {
    license = 'BC'
    confidence = 1
  } else {
    license = str_remove(string = license_text[1],
                         pattern = 'License:\\s+') %>%
      str_trim()
    confidence = 1
    }
  output = output %>%
    mutate(license = license,
           confidence = confidence)
  license_text
  list.files('./data/oss/original/Julia/Licenses')[1]
  getwd()
  owner = str_extract(string = textfile, pattern = '(?<=/)[:alnum:]+(?=_)')
  name = str_extract(string = textfile, pattern = str_c('(?<=_).*(?=.txt)'))
  print(textfile)
  license_text = readLines(con = textfile)
  if (is_empty(x = license_text)) {
    output = data.table(owner = owner,
                        name = name,
                        license = NA,
                        confidence = NA)
  } else if (str_detect(string = license_text[1], pattern = '^License:\\s+NOASSERTION$')) {
    output = data.table(owner = owner,
                        name = name,
                        license = str_extract(string = license_text[7],
                                              pattern = '.*(?= similarity)') %>%
                          str_trim(),
                        confidence = str_extract(string = license_text[7],
                                                 pattern = '\\d{2,3}.\\d{2}') %>%
                          as.numeric() / 1e2)
  } else if (str_detect(string = license_text[1], pattern = '^License:\\s+None$')) {
    output = data.table(owner = owner,
                        name = name,
                        license = 'BC',
                        confidence = 1)
  } else {
    output = data.table(owner = owner,
                        name = name,
                        license = str_remove(string = license_text[1],
                                             pattern = 'License:\\s*'),
                        confidence = str_extract(string = license_text[5],
                                                 pattern = '\\d{2,3}.\\d{2}') %>%
                          as.numeric() / 1e2)
  }
  return(value = output)
}

maybe = map_df(.x = str_c('./data/oss/original/Julia/Licenses/',
                          list.files(path = './data/oss/original/Julia/Licenses/')),
               .f = parse_license_type)

maybe = parse_license_type(textfile = './data/oss/original/Julia/Licenses/JuliaFEM_AbaqusReader.txt')
maybe2 = parse_license_type(textfile = './data/oss/original/Julia/Licenses/gcalderone_AbbrvKW.txt')


getwd()
list.files('./data/oss/original/Julia/Licenses/')
read.table('/data/oss/data/original/Julia/Licenses/path.txt')


for (i in 1:nrow(pkg_licenses)) {
  license_text = pkg_licenses$license_text[i]
  system(command = str_c('OCTOKIT_ACCESS_TOKEN=',
                         Github_API_token,
                         ' licensee detect ',
                         lice
                         
  str_c('/data/oss/original/Julia/Licenses/',
        julia_packages$owner[i],
        '/',
        julia_packages$name[i],
        '.txt')
}
```

For each package we want to obtain certain variables. One variable of interest is the license, attribution, and year. In order to obtain the license information we used the [Github API](https://developer.github.com/v3/) to obtain the license type. When Github has detected a license type we use the identified license type. When a repository has no license file, we assume the default Berne Convention applicable "All rights reserved" license. For the majority of the projects, there is a license file which has not been identified, in those cases we employed a license classification tool: the Ruby gem [Licensee](https://github.com/benbalter/licensee).

In order to assess the quality of our methodology, we downloaded all the license files for Github repositories and saved them locally to inspect and extract additional information.

```{r}
fetch_license_text = function(julia_pkgs) {
  #' Verifies the Github detected license for the repository and the text.
  #'
  #' @description Uses the Github API to get the detected license and source.
  #' @param `julia_pkgs` a data.frame with the owner and name (without .jl).
  #' @usage owner_name_repo(julia_pkgs)
  #' @return Writes the data to 'id.prj_licenses'
  # Helper
  helper = function(owner, name) {
    output = data.table(name = name, license = NA)
    license_file = str_c('https://api.github.com/repos/',
                         owner,
                         '/',
                         name,
                         '.jl/license') %>%
      # This is my Personal Token for this project.
      GET(add_headers(Authorization = str_c('token ', Github_API_token))) %>%
      content(as = 'text', encoding = 'UTF-8') %>%
      fromJSON()
    if (all(names(license_file) %in% c('message', 'documentation_url'))) {
      if (license_file$message %in% 'Not Found') {
        # Berne Convention standard terms
        return(value = data.table(name = name,
                                  license_type = 'BC',
                                  license_text = 'All rights reserved'))
        }
      }
    license_text = license_file$download_url %>%
      GET() %>%
      content(as = 'text', encoding = 'UTF-8')
    output = data.table(name = name,
                        license_type = ifelse(test = is.null(license_file$license$spdx_id),
                                              yes = NA,
                                              no = license_file$license$spdx_id),
                        license_text = license_text)
    return(value = output)
  }
  output = pmap_dfr(.l = julia_pkgs %>%
                    filter(available & (remote_platform %in% 'github.com')) %>%
                    select(owner, name),
                    .f = helper)
  conn = con_db(pass = get_my_password())
  dbWriteTable(conn = conn,
               name = 'prj_licenses',
               value = output,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(dbDisconnect(conn = conn))
  }
fetch_license_text(julia_pkgs = julia_pkgs)
pkg_licenses = function() {
  conn = con_db(pass = get_my_password())
  output = dbReadTable(conn = conn,
                       name = 'prj_licenses')
  on.exit(dbDisconnect(conn = conn))
  return(value = output)
  }
pkg_licenses = pkg_licenses()

```

# Identified Production-Ready and Maintained Packages

1. Depreciated packages are those identified by any of the three conditions:

- Has been migrated to `JuliaArchive`

- It is explicitly stated in the definition

- It redirects to a different package

```{r}
basic_information = basic_information %>%
  mutate(Package_Status = 'Maintained') %>%
  mutate(Package_Status = ifelse(test = (Owner == 'JuliaArchive') |
                                   str_detect(string = Description,
                                              pattern = '(?i)(deprecated)'),
                                 yes = 'Deprecated',
                                 no = Package_Status))
```

2. In order to exclude pre-production packages, depreciated, or abandoned packages, I use the following criteria:

- It passes all tests for the current released version (Julia 0.6) based on [PackageEvaluator](https://github.com/JuliaCI/PackageEvaluator.jl)

- At some point it has worked with Julia 0.6 (some release has work with some version of dependencies)

- Out of the last 25 builds using Travis C.I., some job has been successful with Julia 0.6 (some branch works even if it has not been released)

If a package meets any of the three criterias it is assumed to be production ready and maintained.

```{r}
pkg_eval = function(name) {
  #' Works with current version.
  #'
  #' @description Passed PackageEvaluator with flying colors in current release.

  #' @usage pkg_eval(name)
  #' @return logit indicator
  str_c('https://pkg.julialang.org/logs/', name, '_0.6.log') %>%
    GET() %>%
    content(as = 'text') %>%
    str_detect(pattern = str_c(name, ' tests passed'))
}
some_release = function(name) {
  #' Has the package ever worked with any currently supported versions?
  #'
  #' @description Verifies if any release passed its tests for Julia 0.6.

  #' @usage some_release(name)
  #' @return logit indicator
  str_c('https://pkg.julialang.org/detail/', name) %>%
    GET() %>%
    content(as = 'text') %>%
    str_remove_all(pattern = '\n') %>%
    str_detect(pattern = '(?<=<h4>Julia v0.6</h4>\\s{4}<pre>).*(?=</pre>\\s{8}<h4>)')
  }
stable_last = function(repo) {
  #' Does the last working build job (within the last 25 jobs) include 0.6?
  #'
  #' @description Has it passed with Julia 0.6.

  #' @usage stable_last(name)
  #' @return logit indicator
  repo = str_extract(string = repo,
                     pattern = '(?<=.com/).*.jl?')
  if (is.na(x = repo)) {
    return(FALSE)
  }
  builds = GET(url = str_c('https://api.travis-ci.org/repos/', repo, '/builds'),
               add_headers(c(Accept = 'application/json',
                             Authorization = 'token DRt1TjjDmPG4wX8bq0YqVg'))) %>%
    content(as = 'text', encoding = 'UTF-8') %>%
    fromJSON()
  if (is_empty(x = builds)) {
    return(FALSE)
  }
  builds = builds %>%
    filter(result == 0L)
  if (is_empty(x = builds)) {
    return(FALSE)
  }
  builds = builds %>%
    head(1L) %>%
    getElement(name = 'id')
  output = '0.6' %in%
    (GET(url = str_c('https://api.travis-ci.org/builds/', builds),
         add_headers(c(Accept = 'application/json',
                       Authorization = 'token DRt1TjjDmPG4wX8bq0YqVg'))) %>%
       content(as = 'text', encoding = 'UTF-8') %>%
       fromJSON() %>%
       getElement(name = 'config') %>%
       getElement(name = 'julia'))
  return(output)
}
```
